Luminance constancy under fixed geometry

### 2018-04-24 Draft4/draft4.tex
more edits

Next we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
This is a more realistic condition, where the spectra of light sources change while the objects remain fixed, as in a naturalistic scene. 
Similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
First we trained and evaluated AMA on the cone responses to the image patches.
Figure~\ref{fig:isomerizationFails} shows the responses of the first two receptive fields to all the image patches in the training set.
For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
The decoding performance using these receptive fields for the test set is shown in Figure~\ref{fig:IsomerizationResults}.

@@

\subsubsection{Condition 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
% Figure condition 3
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_b.pdf}
        \label{fig:case12Results}
    \end{subfigure}
    \caption{{\bf Condition 3:} (a) Target LRV estimates v/s assigned luminance for images in condition 3. The AMA estimates are unbiased and have smaller relative error compared to linear model.}
    \label{fig:case12AllResults}
\end{figure}

>>>>

Next we discuss Condition 2, where the spectral power distribution function of the light sources and the target object LRV and relative spectrum varies. 
This is a more naturalistic condition compared to condition 1.
Again, similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
First we trained and evaluated AMA on the cone responses to the image patches.
Figure~\ref{fig:isomerizationFails} shows the responses of the first two receptive fields to all the image patches in the training set.
For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
The decoding performance using these receptive fields for the test set is shown in Figure~\ref{fig:IsomerizationResults}.

@@

\subsubsection{Condition 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
% Figure condition 3
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \caption{LRV estimates}
        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_a.pdf}
        \label{fig:case12Results}
    \end{subfigure}
    \caption{{\bf Condition 3:} Target LRV estimates v/s assigned luminance for images in test set of condition 3. The LRV estimates have been obtained using RFs learnt on contrast normalized images. The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.}
    \label{fig:case12AllResults}
\end{figure}
